\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2013-01-10 paper/mswp2012-proposal.tex
added Communication Lines

The \textbf{project manager} will be the head of the project and will be assisted by his co project manager during all phases and as a backup in case of unforseeable circuumstances. One of them should also have a funded technical knowledge, the other expirenced in economical topics. Both should work as a team and also handle the ressource management and trigger the planned phases. \\

Another very importent rule to fill will be the \textbf{Quality manager}. This person will create the quality plan, organize reviews and check, if the corresponding plan is also executed like intended. \\

@@

\subsubsection{Dev Team}
There will be several Dev Teams with different main aspects to cover, but whatsoever there will be couple of poeple that will be responsible for small parts of each team.

@@

Additional a \textbf{Mobile Dev Team} will join to implment mobile clients for the project. Only iOS and Android clients are planned until version 2.0 therefore knowledge in iOS and/or Android programming is mandatory. The size of this team should be between \textbf{three and five people}.

@@

\subsubsection{Communication and Documentation}
For each team there will be a seperate mailing list to distribute messages to the whole team.

@@

The official blog will be used as communication channel to the users and the community and will also be used to publish scientifical relevant results from the research group as well as results from user interviews. \\

The created project documentation will be stored in the configuration management tool, which will also handle access control and versioning. This tool will be set up by the strategy team before the project start.

>>>>

The \textbf{project manager} will be the head of the project and will be assisted by his co project manager during all phases and as a backup in case of unforeseeable circumstances. One of them should also have a funded technical knowledge, the other experienced in economical topics. Both should work as a team and also handle the resource management and trigger the planned phases. \\

Another very important rule to fill will be the \textbf{Quality manager}. This person will create the quality plan, organize reviews and check, if the corresponding plan is also executed like intended. \\

@@

\subsubsection{Dev Team}
There will be several Dev Teams with different main aspects to cover, but whatsoever there will be couple of people that will be responsible for small parts of each team.

@@

Additional a \textbf{Mobile Dev Team} will join to implement mobile clients for the project. Only iOS and Android clients are planned until version 2.0 therefore knowledge in iOS and/or Android programming is mandatory. The size of this team should be between \textbf{three and five people}.

@@

\subsubsection{Communication and Documentation}
For each team there will be a separate mailing list to distribute messages to the whole team.

@@

The official blog will be used as communication channel to the users and the community and will also be used to publish scientifically relevant results from the research group as well as results from user interviews. \\

The created project documentation will be stored in the configuration management tool, which will also handle access control and versioning. This tool will be set up by the strategy team before the project start. \\

All members of every project team has to satisfy the line of communication. Every requests or problems should be discussed within the team and with the responsible team leader. Project leader itself will handle the requests from their team members or forward the problem to the project manager. If a big problem comes into being, it will be redirected to the management of the company.
